Digital History in Finland, 1488-1828

### 2016-06-29 inst/examples/manuscript-krakow.Rmd
Rmd update

# Read data
fen <- readRDS("df.Rds")
kun <- readRDS("../../../kungliga/antagomir/df.Rds")

fenraw <- readRDS("df.raw.Rds")
kunraw <- readRDS("../../../kungliga/antagomir/df.raw.Rds")

>>>>

# Read data
fen <- readRDS("df.Rds")
kun <- readRDS("../../../kungliga/df.Rds")

fenraw <- readRDS("df.raw.Rds")
kunraw <- readRDS("../../../kungliga/df.raw.Rds")
